Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
style edit: relabeled Prop 6 Case 1 zeta and zeta_2 to become: zeta_2 and zeta_3

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1}.
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
	\begin{equation}
	\max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$. First, consider $I^{\bar{b}_2}_1$. Let $\zeta_2 := c_u / 2$. Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
	\begin{IEEEeqnarray*}{c}
		c_u - \zeta_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_2,\\
		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_2, \quad \text{and} \quad 
		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_2.
	\end{IEEEeqnarray*}
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
	\begin{IEEEeqnarray}{rCl}
		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0, \nonumber
		\label{eq:I1_b2_bar_infinity}
	\end{IEEEeqnarray} 
	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 := \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$. Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.

>>>>

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1}.
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
	\begin{equation}
	\max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta_2: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta_2 (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$. First, consider $I^{\bar{b}_2}_1$. Let $\zeta_3 := c_u / 2$. Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
	\begin{IEEEeqnarray*}{c}
		c_u - \zeta_3 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_3,\\
		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_3, \quad \text{and} \quad 
		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_3.
	\end{IEEEeqnarray*}
	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
	\begin{IEEEeqnarray}{rCl}
		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0, \nonumber
		\label{eq:I1_b2_bar_infinity}
	\end{IEEEeqnarray} 
	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$. Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
